\documentclass[11pt, addpoints, answers]{exam}

\usepackage{amsmath, amssymb, amsthm, euler}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{tikz}
\usepackage{tikz-qtree}
\usetikzlibrary{graphs}
\tikzset{every tree node/.style={minimum width=2em,draw,circle},
    blank/.style={draw=none},
    edge from parent/.style=
    {draw,edge from parent path={(\tikzparentnode) -- (\tikzchildnode)}},
    level distance=1.2cm}
\usepackage{listings}   
\usepackage{caption}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{underscore}
% \usepackage[top=2cm, bottom=2cm, left=2cm, right=2cm]{geometry}  
\makeatletter
\newcommand\dlmu[2][2.5cm]{\hskip1pt\underline{\hb@xt@ #1{\hss#2\hss}}\hskip3pt}
\makeatother

% For inserting code snippets.
\usepackage{listings}
\lstset{
    columns = fixed,
    basewidth = {0.5em},
    breaklines = true,
    backgroundcolor = \color{white},
    keywordstyle = \color[RGB]{40, 40, 255},
    numberstyle = \footnotesize\color{darkgray},
    commentstyle = \ttfamily\color{violet},
    basicstyle = \ttfamily,
    stringstyle = \ttfamily\color[RGB]{128, 0, 0},
    showstringspaces = false,
    language = {[11]C++},
    escapechar = \@
}
\lstnewenvironment{cpp}[1][]{\lstset{language = {[11]C++}, #1}}{}

\usepackage{tikz}

% headers, footers, titles
\newcommand{\CourseName}{CS101 Algorithms and Data Structures}
\newcommand{\HomeworkNO}{Homework 10}
\newcommand{\DueDate}{Due date: 23:59, December 4th, 2022}

\pagestyle{headandfoot}
\runningheadrule
\runningheader{\CourseName}{\HomeworkNO}{\DueDate}
\runningfooter{}{\thepage}{}

\title{
	\CourseName\\
	Fall 2022\\
	\HomeworkNO
}
\author{}
\date{\DueDate}

% formats of questions, choices, points, etc.
\qformat{\bf\thequestion. (\totalpoints\ points) \thequestiontitle\hfill}
\pointname{'}
\CorrectChoiceEmphasis{\bf\color{blue}}
\SolutionEmphasis{\color{blue}}

% We frequently use this font.
\newcommand{\ttt}{\texttt}

\begin{document}

\maketitle

\begin{enumerate}
	\item Please write your solutions in English.
	\item Submit your solutions to gradescope.com.
	\item Set your FULL name to your Chinese name and your STUDENT ID correctly in Account Settings.
	\item If you want to submit a handwritten version, scan it clearly. \ttt{CamScanner} is recommended.
	\item When submitting, match your solutions to the problems correctly.
	\item No late submission will be accepted.
	\item Violations to any of the above may result in zero points.
\end{enumerate}

\begin{questions}

\include{multipleChoices}

\newpage

\include{shortestPath}

\newpage

\include{Astar}

\newpage

\include{FloydWarshall}


\end{questions}

\end{document}