\titledquestion{Multiple Choices}

Each question has \textbf{one or more} correct answer(s). Select all the correct answer(s). For each question, you will get 0 points if you select one or more wrong answers, but you will get half points if you select a non-empty subset of the correct answers.

Write your answers in the following table.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Note: The `LaTeX' way to answer a multiple-choices question is to replace `\choice'
% with `\CorrectChoice', as what you did in the first question. However, there are still
% many students who would like to handwrite their homework. To make TA's work easier,
% you have to fill your selected choices in the table below, no matter whether you use 
% LaTeX or not.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}[h]
    \centering
    \renewcommand{\arraystretch}{1.25}
    \begin{tabular}{|p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|}
        \hline 
        (a) & (b) & (c) & (d) & (e) & (f) \\
        \hline
        % YOUR ANSWER HERE.
        &  &  &  &  &  \\

        \hline
    \end{tabular} 
\end{table}

\begin{parts}

    \part[2] A union tree, used in a disjoint set with only union-by-rank optimization, has height 7. The number of nodes contained in that tree \textbf{can not} be:
    \begin{choices}
        \choice 127
        \choice 128
        \choice 129
        \choice 2024
    \end{choices}

    \part[2] Which of the following statements are true for disjoint set?
    \begin{choices}
        \choice The two main operations of disjoint set are Find and Union.
        \choice Union-by-rank optimization alone is sufficient to ensure that the height of the union trees remains $O(\alpha(n))$, where $n$ is the number of nodes and $\alpha$ is the inverse Ackermann function.
        \choice After applying the Find operation with path compression in a disjoint set, the height of the union tree will always decrease.
        \choice The combination of path compression and union by rank ensures that both the time complexity of the Find and Union operations is nearly constant in practice.

    \end{choices}

    \part[2] Undirected Graph $G = (V, E)$ is stored in an adjacency matrix $A$. We let $A_{i, j}=1$ if and only if there is an edge between $V_i$ and $V_j$ in G, otherwise $A_{i,j}=0$. We want to know whether there is a path \textbf{with length $m$} between $V_i$ and $V_j$ by visiting $P_{i,j}$; if $P_{i,j}$=0, then there is no such path. What should $P$ be?
    \begin{choices}
    	\choice $A$
    	\choice $mA$
    	\choice $A^{m-1}$
    	\choice $A^m$
    \end{choices}

    \part[2]  Which of the following statements are true for graph properties?
    \begin{choices}
        \choice An undirected simple graph with $n$ vertices can have at most $n(n-1)$ edges.
        \choice An undirected graph is acyclic if and only if it is a tree.
        \choice The minimum number of edges required to connect $n$ vertices in a graph is $n - 1$.
        \choice In a connected undirected graph, the removal of any edge will always result in a graph that is still connected.
    \end{choices}

    \part[2] Which of the following statements are true for graph properties?
    \begin{choices}
        \choice Any tree is a bipartite graph.
        \choice A graph with an odd number of vertices can not be a bipartite graph.
        \choice A DAG(Directed Acyclic Graphs) must have at least one vertex with no incoming edges (source).
        \choice The sum of the degrees of all vertices in a graph is always equal to the number of edges in the graph.
    \end{choices}

    \part[2] Which of the following statements are true for graph traversal?
    \begin{choices}
        \choice Given two vertices $s$ and $t$ in a graph $G$, we can use both BFS and DFS to determine whether there exists a path from $s$ to $t$.
        \choice Both the time complexity of DFS and that of BFS are $\Theta(|V| + |E|)$.
        \choice In DFS, all vertices are visited in the order of their distance from the start vertex.
        \choice In BFS, let $d(v)$ be the minimum number of edges between a vertex $v$ and the start vertex. For any two vertices $u$ and $v$ in the queue, $|d(u) - d(v)|$ is always less than $2$.
    \end{choices}
    

\end{parts}