\titledquestion{Counting Jewelry Pairs}

Astra opens up a jewelry store to sold the jewelry. Each jewelry has a distinct positive "beauty value" $a_i$, where $i$ means it's the $i$-th jewelry Astra got. You are asked to help Astra to solve the problems for her customs.

\begin{parts}
\part{} 

Breach wants to buy a pair of jewelry, where jewelry found earlier should be more beautiful i.e. have a bigger beauty value. In other words, the pair contains $2$ jewelry $i$ and $j$, where $i<j,a_j<a_i$. \\
Astra needs to count the number of jewelry pairs satisfying Breach's requirement.

\begin{subparts}
    \subpart[1] Recall what is told in class. This problem is equivalent to \\
    \begin{oneparcheckboxes}
        \choice Quick Sort
        \choice Merge Sort
        \choice Counting Inversions
        \choice Binary Search
    \end{oneparcheckboxes}
    \subpart[2] Briefly write how to solve this problem using divide and conquer.
\begin{solution}
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\end{solution}
\end{subparts}
\newpage
\noindent \textbf{In the two questions below, you are allowed to describe your algorithm by modifying parts of the algorithm in $(a).ii$. 
} 
\part{}

Chamber wants to buy a pair of jewelry too. His requirement is precise: He wants that the earlier found jewelry is "quadratic more beautiful" than the other one. In other words, for two jewelry $i$ and $j(i<j)$, Chamber wants $a_i>\alpha a_j^2+\beta a_j + \gamma$, where $a_i,a_j$ is the "beauty value" of $i/j$-th jewelry and $\alpha,\beta>0$.\\
Astra needs to count the number of jewelry pairs satisfying Chambers's requirement.

You should :
\begin{subparts}
  \subpart[4]Describe your algorithm, either by modifying or rewriting one.
    \begin{solution}
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
    \end{solution}
    \subpart[2] Justify why your algorithm is correct and analyze the time complexity. 
    \begin{solution}
\\
\\
\\
\\
\\
\\
\\
\\
    \end{solution}
\end{subparts}

\newpage
\part{} Cypher also wants to buy a pair of jewelry, too. Cypher wants to find the relation of "beauty value" between different jewelry. He wants that the difference of when the jewelry was found and the difference of beauty value are closed. In other words, for two jewelry $i$ and $j(i<j)$, Cypher wants $a_i- a_j>\alpha|i-j|$, where $a_i,a_j$ is the "beauty value" of $i/j$-th jewelry and $\alpha>0$.\\
Astra needs to count the number of jewelry pairs satisfying Cypher's requirement.

You should :
\begin{subparts}
  \subpart[4]Describe your algorithm, either by modifying or rewriting one.
    \begin{solution}
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
    \end{solution}
    \subpart[2] Justify why your algorithm is correct and analyze the time complexity. 
    \begin{solution} 
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
    \end{solution}
\end{subparts}
\end{parts}