\titledquestion{Multiple Choices}

Each question has \textbf{one or more} correct answer(s). Select all the correct answer(s). For each question, you will get 0 points if you select one or more wrong answers, but you will get 1 point if you select a non-empty subset of the correct answers.

Write your answers in the following table.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Note: The `LaTeX' way to answer a multiple-choices question is to replace `\choice'
% with `\CorrectChoice', as what you did in the previous questions. However, there are 
% still many students who would like to handwrite their homework. To make TA's work 
% easier, you have to fill your selected choices in the table below, no matter whether 
% you use LaTeX or not.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}[htbp]
	\centering
	\begin{tabular}{|p{2cm}|p{2cm}|p{2cm}|p{6cm}|}
		\hline
		(a) & (b) & (c) \\
		\hline
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		% YOUR ANSWER HERE.
		  BD  &  AC   &  C   \\
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\hline
	\end{tabular}
\end{table}

\begin{parts}
	\part[2] A problem in $\NP$ is $\NPC$ if:
	\begin{choices}
		\choice It can be reduced to another $\NPC$ problem in polynomial time.
		\CorrectChoice There exists a $\NPC$ problem which can be reduced to it in polynomial time.
		\choice It can be reduced to any other $\NP$ problem in polynomial time.
		\CorrectChoice Any other $\NP$ problem can be reduced to it in polynomial time.
	\end{choices}


	\part[2] Assuming that $\P\neq\NP$, which of the following problems are in $\NPC$?
	You may search the Internet for more information if you are unfamiliar with the problems.
	\begin{choices}
		\CorrectChoice \texttt{LONG-PATH}: $(G,s,t,k)$ Given an undirected graph $G$,
		determine whether there exists a simple path from \(s\) to \(t\) whose length is greater or equal to $k$.
		\choice \texttt{HALTING}: $(P,I)$ Given a compilable C++ program $P$ and the input $I$ for $P$,
		determine if $P$ runs infinitely on $I$.
		\CorrectChoice \texttt{4-SAT}: $\phi$ Given a CNF (conjunction normal form)
		where each clause is the disjunction of exactly 4 literals,
		determine whether $\phi$ is satisfiable.
		\choice \texttt{PRIME}: $n$ Given a positive integer $n$, determine whether it is a prime number.
	\end{choices}

	\part[2] For two decision problems $A$ and $B$, suppose that $A\leq_p B$.
	Which of the following statements are true?
	(Hint: there exists complexity classes that are strictly bigger than $\NP$)
	\begin{choices}
		\choice $A\in \P \implies B\in \P$
		\choice $A\in \NPC\implies B\not\in \NPC$.
		\CorrectChoice $B\in \P\implies A\in \P$.
		\choice $B\in \NPC\implies A\in \NPC$.
	\end{choices}

\end{parts}
