\documentclass[11pt, addpoints, answers]{exam}

\usepackage{amsmath, amssymb, euler}
\usepackage{xcolor}
\usepackage{algorithm, algorithmicx, algpseudocode}
\usepackage{tikz, tikz-qtree, drawstack}
\usepackage[shortlabels]{enumitem}

\usetikzlibrary{graphs}
\tikzset{every tree node/.style={minimum width=2em,draw,circle},
	blank/.style={draw=none},
	edge from parent/.style=
	{draw,edge from parent path={(\tikzparentnode) -- (\tikzchildnode)}},
	level distance=1.2cm}

% For inserting code snippets.
\usepackage{listings}
\lstset{
    columns = fixed,
    basewidth = {0.5em},
    breaklines = true,
    backgroundcolor = \color{white},
    keywordstyle = \color[RGB]{40, 40, 255},
    numberstyle = \footnotesize\color{darkgray},
    commentstyle = \ttfamily\color{violet},
    basicstyle = \ttfamily,
    stringstyle = \ttfamily\color[RGB]{128, 0, 0},
    showstringspaces = false,
    language = {[11]C++},
    escapechar = \@
}
\lstnewenvironment{cpp}[1][]{\lstset{language = {[11]C++}, #1}}{}

\usepackage{tikz}

% headers, footers, titles
\newcommand{\CourseName}{CS101 Algorithms and Data Structures}
\newcommand{\HomeworkNO}{Homework 4}
\newcommand{\DueDate}{Due date: 23:59, October 16th, 2022}

\pagestyle{headandfoot}
\runningheadrule
\runningheader{\CourseName}{\HomeworkNO}{\DueDate}
\runningfooter{}{\thepage}{}

\title{
	\CourseName\\
	Fall 2022\\
	\HomeworkNO
}
\author{}
\date{\DueDate}

% formats of questions, choices, points, etc.
\qformat{\bf\thequestion. (\totalpoints\ points) \thequestiontitle\hfill}
\pointname{'}
\CorrectChoiceEmphasis{\bf\color{blue}}

% We frequently use this font.
\newcommand{\ttt}{\texttt}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}
\newcommand{\bluett}[1]{\blue{\ttt{#1}}}

\begin{document}

\maketitle

\begin{enumerate}
	\item Please write your solutions in English.
	\item Submit your solutions to gradescope.com.
	\item Set your FULL name to your Chinese name and your STUDENT ID correctly in Account Settings.
	\item If you want to submit a handwritten version, scan it clearly. \ttt{CamScanner} is recommended.
	\item When submitting, match your solutions to the problems correctly.
	\item No late submission will be accepted.
	\item Violations to any of the above may result in zero points.
\end{enumerate}

\newpage


{\large\textbf{Notes}:}

\begin{enumerate}
	\item Some problems in this homework requires you to design Divide and Conquer algorithm. When grading these problems, we will put more emphasis on how you reduce a problem to a smaller size problem and how to combine their solutions with Divide and Conquer strategy. 
	\item Your answer for these problems {\color{red}\textbf{should}} include:
	\begin{enumerate}
		\item {\color{red}Algorithm Design}
		\item {\color{red}Time Complexity Analysis}
		\item Pseudocode (Optional)
	\end{enumerate}
    \item Your answer for these problems is {\color{red}not allowed to include real C or C++ code}.
	\item In Algorithm Design, you should describe each step of your algorithm clearly.
	\item Unless required, writing pseudocode is optional. If you write pseudocode, please give some additional descriptions if the pseudocode is not obvious.
	\item You are recommended to finish the algorithm design part of this homework with \LaTeX.
\end{enumerate}

\newpage

\begin{questions}

\include{example}

\newpage

\include{trees}

\newpage

\include{tree_properties}

\newpage

\include{tree_structure_and_traversal}

\newpage

\include{recurrence_relations}

\newpage

\include{maximum_contiguous_subsequence_sum}

\newpage

\include{kth_min}

\end{questions}

\end{document}