\titledquestion{Multiple Choices}

Each question has \textbf{one or more} correct answer(s). Select all the correct answer(s). For each question, you will get 0 points if you select one or more wrong answers, but you will get 1 point if you select a non-empty subset of the correct answers.

Write your answers in the following table.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Note: The `LaTeX' way to answer a multiple-choice question is to replace `\choice'
% with `\CorrectChoice', as what you did in the first question. However, there are still
% many students who would like to handwrite their homework. To make TA's work easier,
% you have to fill in your selected choices in the table below, no matter whether you use 
% LaTeX or not.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}[htbp]
	\centering
	\begin{tabular}{|p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|}
		\hline 
		(a) & (b) & (c) & (d) & (e) & (f) \\
		\hline
  		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		% YOUR ANSWER HERE.
		   &  &  &  &  &  \\
            %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\hline
	\end{tabular} 
\end{table}

\begin{parts}


\part[2] Which of the following statements about heaps are true?

\begin{choices}
    \choice In a complete binary min-heap, the sum of values of the internal nodes is no greater than that of leaf nodes. 
    \choice We can build a heap from an array in linear time through Floyd's method, so we can sort an array in linear time through heap sort.
    \choice If we use a min-heap to do heap sort, we can sort an array in increasing order.
    \choice For any node $a$ in a heap, the subtree of the tree with root $a$ is still a heap. 
\end{choices}

\part[2] Which of the following statements about the Huffman Coding Algorithm are true?

\begin{choices}
    \choice Huffman Coding Algorithm is a compression method without information loss.
    \choice If character $a$ has a higher frequency than $b$, then the encoded $a$ has a length no longer than encoded $b$.
    \choice The Huffman Coding Tree is a complete binary tree.
    \choice Given the set of characters and the order of their frequencies but the exact frequencies unknown, we can still determine the length of each encoded character.
\end{choices}

\part[2] Which of the following can be a set of decoded characters in the Huffman Coding Algorithm?

\begin{choices}
    \choice $\{0,10,110,1110,11110,111110\}$
    \choice $\{00,0100,0101,011,10,11\}$
    \choice $\{0,100,101,10,11\}$
    \choice $\{00,010,011,110,111\}$
\end{choices}

\part[2] Suppose there are two arrays: $\{a_i\}_{i=1}^n$ is an \textbf{ascending} array with $n$ distinct elements. $\{b_i\}_{i=1}^n$ is the reverse of $a$, i.e. $b_i=a_{n-i+1}$. Which of the following statements is true?

\begin{choices}
    \choice If we run Floyd's method to build a min-heap for each of the two arrays, the resulting heap will be the same.
    \choice If we build a complete binary min-heap by inserting $a_i$ sequentially into an empty heap, the runtime of this process is $\Theta(n)$.
    \choice If we build a complete binary min-heap by inserting $b_i$ sequentially into an empty heap, the runtime of this process is $\Theta(n)$.
    \choice If we run heap sort on $\{b_i\}_{i=1}^n$, the runtime is $\Theta(n)$.
    
\end{choices}

\part[2] Which of the following statements about BST are true?

\begin{choices}
    \choice For a BST, the newly inserted node will always be a leaf node.
    \choice Given an array, suppose we construct a BST (without balancing) by sequentially inserting the elements of the array into an empty BST. Then the time complexity of this process is $O(n\log n)$ in all cases.
    \choice Given a BST with member variable \ttt{tree\_size} (the number of descendants of this node) and a number $x$, we can find out how many elements in the BST is less than $x$ in $O(h)$ time where $h$ is the height of the BST.
    \choice If a BST is constructed by inserting elements in a random order, the expected height of the tree is $O(\log n)$.
\end{choices}

\part[2] Which of the following statements about BST are true?

\begin{choices}
    \choice In a BST, the nodes in a subtree appear contiguously in the in-order traversal sequence of the BST.
    \choice If a node doesn't have a right subtree, then its \textbf{next} (defined in lectures) object is the largest object (if any) that exists in the path from the node to the root.
    \choice  In a BST, the pre-order traversal sequence can uniquely determine the structure of the tree.
    \choice  In a BST, the sum of the heights of all nodes is minimized when the tree is perfectly balanced.
\end{choices}


    
\end{parts}

