\documentclass[11pt, addpoints, answers]{exam}

\usepackage{amsmath, amssymb}
\usepackage{xcolor}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{tikz}
\usepackage{tikz-qtree}
\usepackage{subfigure}
\usetikzlibrary{positioning}
\usetikzlibrary{graphs}
\usetikzlibrary{arrows.meta}

\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}

% For inserting code snippets.
\usepackage{listings}
\lstset{
    columns = fixed,
    numbers=left,
    basewidth = {0.5em},
    breaklines = true,
    backgroundcolor = \color{white},
    keywordstyle = \color[RGB]{40, 40, 255},
    numberstyle = \footnotesize\color{darkgray},
    commentstyle = \ttfamily\color{violet},
    basicstyle = \ttfamily,
    stringstyle = \ttfamily\color[RGB]{128, 0, 0},
    showstringspaces = false,
    language = {[11]C++},
    escapechar = \@
}
\lstnewenvironment{cpp}[1][]{\lstset{language = {[11]C++}, #1}}{}

\renewcommand{\baselinestretch}{1.15}
\setlength{\parskip}{1.25\baselineskip}

\usepackage{tikz}
\usepackage{tikz-qtree}
\tikzset{every tree node/.style={minimum width=2em,draw,circle},
    blank/.style={draw=none},
    edge from parent/.style=
    {draw,edge from parent path={(\tikzparentnode) -- (\tikzchildnode)}},
    level distance=1.2cm}


% headers, footers, titles
\newcommand{\CourseName}{CS101 Algorithms and Data Structures}
\newcommand{\HomeworkNO}{10}
\newcommand{\DueDate}{December 13, 2024}

\pagestyle{headandfoot}
\runningheadrule
\runningheader{CS101 Fall24}{Homework \HomeworkNO}{Due on: \DueDate}
\runningfooter{}{\thepage}{}

\title{
    \vspace{25pt}
    \LARGE ShanghaiTech University \\
    \bigskip
    \textbf{\CourseName} \\
    \textbf{Fall 2024}   \\
    \bigskip
    Homework \HomeworkNO
}
\author{}
\date{Due date: \DueDate, at 23:59}

% formats of questions, choices, points, etc.
\qformat{\bf\thequestion. (\totalpoints\ points) \thequestiontitle\hfill}
\pointname{'}
\CorrectChoiceEmphasis{\bf\color{blue}}
\SolutionEmphasis{\color{blue}}

% We frequently use this font.
\newcommand{\ttt}{\texttt}
\newcommand{\bluett}[1]{\textcolor{blue}{\ttt{#1}}}

\newcommand*{\TrueFalse}[1]{%
\ifprintanswers
    \ifthenelse{\equal{#1}{T}}{
        \hfill \parbox[t]{1.50in}{\begin{oneparcheckboxes} \CorrectChoice True \choice False \end{oneparcheckboxes}}
    }{
        \hfill \parbox[t]{1.50in}{\begin{oneparcheckboxes} \choice True \CorrectChoice False \end{oneparcheckboxes}}
    }
\else
    \hfill \parbox[t]{1.50in}{\begin{oneparcheckboxes} \choice True  \choice False \end{oneparcheckboxes}}
\fi
}


\begin{document}

\maketitle

\vspace{50pt}

\begin{enumerate}
    \item Please write your solutions in English.
    \item Submit your solutions to Gradescope.
    \item Set your FULL name to your Chinese name and your STUDENT ID correctly in Gradescope account settings.
    \item If you want to submit a handwritten version, scan it clearly. \ttt{CamScanner} is recommended.
    \item We recommend you to write in \LaTeX.
    \item When submitting, match your solutions to the problems correctly.
    \item No late submission will be accepted.
    \item Violations to any of the above may result in zero points.
\end{enumerate}
\newpage

\begin{questions}


\include{1_multiple_choices}
\include{2_Astar}
\include{3_vertex_weighted_graph}
\include{4_egative_cycle_detection}
\include{5_arbitrage}
\include{6_k_shortest_path}


\end{questions}

\end{document}