\documentclass[11pt, addpoints, answers]{exam}

\usepackage{amsmath, amssymb}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{tikz-qtree}
\usetikzlibrary{positioning}
\usetikzlibrary{graphs}
\usetikzlibrary{arrows.meta}

\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}
% For inserting code snippets.
\usepackage{listings}
\lstset{
    columns = fixed,
    basewidth = {0.5em},
    breaklines = true,
    backgroundcolor = \color{white},
    keywordstyle = \color[RGB]{40, 40, 255},
    numberstyle = \footnotesize\color{darkgray},
    commentstyle = \ttfamily\color{violet},
    basicstyle = \ttfamily,
    stringstyle = \ttfamily\color[RGB]{128, 0, 0},
    showstringspaces = false,
    language = {[11]C++},
    escapechar = \@
}
\lstnewenvironment{cpp}[1][]{\lstset{language = {[11]C++}, #1}}{}

\renewcommand{\baselinestretch}{1.15}
\setlength{\parskip}{1.25\baselineskip}

% headers, footers, titles
\newcommand{\CourseName}{CS101 Algorithms and Data Structures}
\newcommand{\HomeworkNO}{8}
\newcommand{\DueDate}{November 27, 2024}

\pagestyle{headandfoot}
\runningheadrule
\runningheader{CS101 24Fall}{Homework \HomeworkNO}{Due on: \DueDate}
\runningfooter{}{\thepage}{}

\title{
    \vspace{25pt}
    \LARGE ShanghaiTech University \\
    \bigskip
    \textbf{\CourseName} \\
    \textbf{Fall 2024}   \\
    \bigskip
    Homework \HomeworkNO
}
\author{}
\date{Due date: \DueDate, at 23:59}

% formats of questions, choices, points, etc.
\qformat{\bf\thequestion. (\totalpoints\ points) \thequestiontitle\hfill}
\pointname{'}
\SolutionEmphasis{\color{black}}
\CorrectChoiceEmphasis{\bf\color{blue}}



% We frequently use this font.
\newcommand{\ttt}{\texttt}
\newcommand{\bluett}[1]{\textcolor{blue}{\ttt{#1}}}

\begin{document}

\maketitle

\begin{enumerate}
	\item Please write your solutions in English.
	\item Submit your solutions to gradescope.com.
	\item Set your FULL name to your Chinese name and your STUDENT ID correctly in Account Settings.
	\item If you want to submit a handwritten version, scan it clearly. \ttt{CamScanner} is recommended.
	\item When submitting, match your solutions to the problems correctly.
	\item No late submission will be accepted.
	\item Violations to any of the above may result in zero points.
\end{enumerate}

\begin{questions}
	\include{multiple_choices}
    \newpage
    \include{MST}
    \newpage
    \include{machine_learning}
    % Very Easy, Even with just 3 tex!
\end{questions}

\end{document}